---
title: "Bertsimas and Mazumder"
output: html_document
---
Generate example with no outliers and smaller standard deviation on data and errors.
```{r}
gen_sample_test <- function(m,n,i) {
  X <- matrix(rnorm(m*(n-1), sd=1),
              ncol=n-1)
  eps <- rnorm(m, sd=0.1)
  beta <- rep(1, n-1)
  y <- X %*% beta + eps - 1.0
  my_data <- data.frame(y, X)
  write.table(my_data, file=paste("rvd/m",
                                m-length(outliers),
                                "n",n, 
                                "m_outliers", length(outliers), 
                                "i", i, 
                                ".csv",
                                sep=""),
            quote=FALSE,
            row.names=FALSE,
            col.names=FALSE,
            sep=","
  )
}
```



Based on Rousseeuw and Driessen (2006).
```{r}
gen_sample_rvd <- function(m,n,my_pi,i) {
  X <- matrix(rnorm(m*(n-1), sd=10),
              ncol=n-1)
  eps <- rnorm(m, sd=1)
  beta <- rep(1, n-1)
  y <- X %*% beta + eps - 1.0
  outliers <- sample(1:m, size=floor(my_pi*m))
  X[outliers,1] <- X[outliers,1] + rnorm(length(outliers), mean=100,sd=10)
  X <- rbind(X[-outliers,], X[outliers,])
  y <- c(y[-outliers], y[outliers])
  my_data <- data.frame(y, X)
  write.table(my_data, file=paste("rvd/m",
                                m-length(outliers),
                                "n",n, 
                                "m_outliers", length(outliers), 
                                "i", i, 
                                ".csv",
                                sep=""),
            quote=FALSE,
            row.names=FALSE,
            col.names=FALSE,
            sep=","
  )
}
```



Bertsimas and Mazumder (2014)

```{r}
gen_sample <- function(m,n,my_pi,type, i) {
  X <- matrix(rnorm(m*n, sd=100),
              ncol=n)
  eps <- rnorm(m, sd=10)
  beta <- rep(1, n)
  y <- X %*% beta + eps
  outliers <- sample(1:m, size=floor(my_pi*m))
  if (type == "A") {
    X[outliers,1] <- X[outliers,1] + 1000
  } else if (type == "B") {
    x_outliers <- outliers[1:floor(length(outliers)/2)]
    y_outliers <- outliers[(floor(length(outliers)/2)+1):length(outliers)]
    X[x_outliers,1] <- X[x_outliers,1] + 1000
    y[y_outliers] <- y[y_outliers] + 1000
  }
  X <- rbind(X[-outliers,], X[outliers,])
  y <- c(y[-outliers], y[outliers])
  my_data <- data.frame(y, X)
  write.table(my_data, file=paste("bm/m",
                                m-length(outliers),
                                "n",n+1, 
                                "m_outliers", length(outliers), 
                                "i", i, 
                                ".csv",
                                sep=""),
            quote=FALSE,
            row.names=FALSE,
            col.names=FALSE,
            sep=","
  )
}
```



```{r}
set.seed(12345)
for (i in 0:9) {
    gen_sample(201, 5, 0.4, "B", i) # Ex-1
    gen_sample(201, 10, 0.5, "B", i) # Ex-2
    gen_sample(501, 5, 0.4, "A", i) # Ex-3
    gen_sample(501, 10, 0.4, "A", i) # Ex-4
    gen_sample(2001, 10, 0.4, "B", i) # Ex-5
    gen_sample(5001, 10, 0.4, "B", i) # Ex-6
    gen_sample(10001, 20, 0.4, "B", i) # Ex-7
    
    gen_sample_rvd(100, 3, 0.4, i) # RVD
    gen_sample_rvd(100, 5, 0.4, i) # RVD
    gen_sample_rvd(500, 3, 0.4, i) # RVD
    gen_sample_rvd(500, 5, 0.4, i) # RVD
    gen_sample_rvd(1000, 5, 0.35, i) # RVD
    gen_sample_rvd(1000, 10, 0.35, i) # RVD
    gen_sample_rvd(10000, 5, 0.40, i) # RVD
    gen_sample_rvd(10000, 10, 0.40, i) # RVD
    gen_sample_rvd(50000, 5, 0.40, i) # RVD
    
}
```


Real datasets.
For NOxEmissions, row 5404 is an outlier (identified in R package robustbase), but Bertsimas and Mazumder contaminate in a different way.  We will just count it as one of the points like they do.

No indication of which are outliers in  Maronna et al. for alcohol.  

```{r}
attach(NOxEmissions)
dim(NOxEmissions)

for (i in 0:9) {
  X <- NOxEmissions[,c(4,1,3)]
  y <- NOxEmissions[,2]
  m <- nrow(X)
  n <- ncol(X)
  my_pi <- 0.01
  outliers <- sample(1:m, size=floor(my_pi*m))
  x_outliers <- outliers[1:floor(length(outliers)/2)]
  y_outliers <- outliers[(floor(length(outliers)/2)+1):length(outliers)]
  X[x_outliers,1] <- X[x_outliers,1] + 1000
  y[y_outliers] <- y[y_outliers] + 1000
  X <- rbind(X[-outliers,], X[outliers,])
  y <- c(y[-outliers], y[outliers])
  
  my_data <- data.frame(y, X)
  
  write.table(my_data, file=paste("bm-nox/m",
                                  m-length(outliers),
                                  "n",n+1, 
                                  "m_outliers", length(outliers),
                                   "i", i,
                                  "_nox.csv",
                                  sep=""),
              quote=FALSE,
              row.names=FALSE,
              col.names=FALSE,
              sep=","
    )
}
```

